\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fu}

\title{\emph{Forever Undecided} Reading Group \\ Week 2}
\date{}
\author{}
\begin{document}

\maketitle

\section*{Liar Puzzles (Cont.)}

\subsection*{Martians and Venusians}
Suppose that every alien is either a Venusian or a Martian and either left-handed or right-handed. Left-handed Venusians and right-handed Martians always tell the truth, while right-handed Venusians and left-handed Martians always lie. 

\begin{prob}{1.4}
    Martians and Venusians cannot be distinguished from one another by their appearance, nor can left-handed aliens from right-handed ones.
    \begin{enumerate}[a)]
        \item What single question could you ask an alien to determine their handedness?
        \item What about their planet of origin?
        \item Can both handedness and planet of origin be determined from a single question?
        \item What statement could only a left-handed Venusian assert?
        \item What statement could be asserted by any alien?
        \item One alien claims that another is right-handed Venusian while the latter claims that the former is a left-handed Martian. What is the planet of origin and the handedness of each of them?
    \end{enumerate}
\end{prob}

\begin{prob}{1.5}
    Alien couples always consist of one left-handed partner and one-right handed partner.
    \begin{enumerate}[a)]
        \item An alien claims to be from Mars, but their partner claims they're lying. Are these aliens from the same planet?
        \item One member of an alien couple asserts they're both from Venus while the other says that's not true. Which of these aliens is right handed?
        \item One member of another couple says their partner is from Mars. The other says they are both from Mars. What is the planet of origin and the handedness of each of them?
    \end{enumerate}
\end{prob}

\end{document}