\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fu}

\title{\emph{Forever Undecided} Reading Group \\ Week 1}
\date{}
\author{}
\begin{document}

\maketitle

\section*{Liar Puzzles}

\subsection*{Knights and Knaves}
Suppose there is an island where each inhabitant is either a knight, in which case they always tell the truth, or a knave, in which case they always lie.

\begin{prob}{1.1}
    In each case, determine the type of each of the inhabitants involved.
    \begin{enumerate}[a)]
        \item One of a pair of inhabitants claims they're both knaves.
        \item When asked whether they are both knaves, one of another pair of inhabitants answers that at least one of them is.
        \item One of a third pair of inhabitants claims that if they are a knight, then so is the other.
    \end{enumerate}
\end{prob}

\begin{prob}{1.2}
    Prove each of the following:
    \begin{enumerate}[a)]
        \item If an inhabitant of the island asserts ``if I am a knight, then $p$'' then they are indeed a knight, and $p$ is true.
        \item If an inhabitant asserts ``I am a knight if and only if, then $p$'', then $p$ is true.
    \end{enumerate}
\end{prob}

\begin{prob}{1.3}
    You've heard there's gold hidden on the island.
    \begin{enumerate}[a)]
        \item What statement could an inhabitant make from which you could deduce that if they are a knight, then there is gold on the island, but if they are a knave then there might or might not be?
        \item What statement could they make such that you could deduce that if there's gold on the island, then they must be a knight, but if there isn't gold, they could be either a knight or a knave?
        \item An inhabitant tells you they've never claimed there's gold on the island. Later you discover gold there. Were they a knight or a knave?
    \end{enumerate}
\end{prob}

\end{document}