\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fu}

\title{\emph{Forever Undecided} Reading Group \\ Week 1}
\date{}
\author{}
\begin{document}

\maketitle

\section*{Knights and Knaves}
Suppose there is an island where each inhabitant is either a knight, in which case they always tell the truth, or a knave, in which case they always lie.

\begin{prob}{1.1}
    In each case, determine the type of each of the inhabitants involved.
    \begin{enumerate}[a)]
        \item One of a pair of inhabitants claims they're both knaves.
        \item When asked whether they are both knaves, one of another pair of inhabitants answers that at least one of them is.
        \item When a third pair is asked the same question, one of them answers that at least one of them is.
        \item One of a fourth pair of inhabitants claims that if they are a knight, then so is the other.
    \end{enumerate}
\end{prob}

\begin{prob}{1.2}
    Prove each of the following:
    \begin{enumerate}[a)]
        \item If an inhabitant of the island asserts ``if I am a knight, then $p$'' then they are indeed a knight, and $p$ is true.
        \item If an inhabitant asserts ``I am a knight if and only if, then $p$'', then $p$ is true.
    \end{enumerate}
\end{prob}

\begin{prob}{1.3}
    You've heard there's gold hidden on the island.
    \begin{enumerate}[a)]
        \item What statement could an inhabitant make from which you could deduce that if they are a knight, then there is gold on the island, but if they are a knave then there might or might not be?
        \item What statement could they make such that you could deduce that if there's gold on the island, then they must be a knight, but if there isn't gold, they could be either a knight or a knave?
        \item An inhabitant tells you they've never claimed there's gold on the island. Later you discover gold there. Were they a knight or a knave?
    \end{enumerate}
\end{prob}

\pagebreak

\section*{Martians and Venusians}
Suppose that every alien is either a Venusian or a Martian and either left-handed or right-handed. Left-handed Venusians and right-handed Martians always tell the truth, while right-handed Venusians and left-handed Martians always lie. 

\begin{prob}{1.4}
    Martians and Venusians cannot be distinguished from one another by their appearance, nor can left-handed aliens from right-handed ones.
    \begin{enumerate}[a)]
        \item What single question could you ask an alien to determine their handedness?
        \item What about their planet of origin?
        \item Can both handedness and planet of origin be determined from a single question?
        \item What statement could only a left-handed Venusian assert?
        \item What statement could be asserted by any alien?
        \item One alien claims that another is right-handed Venusian while the latter claims that the former is a left-handed Martian. What is the planet of origin and the handedness of each of them?
    \end{enumerate}
\end{prob}

\begin{prob}{1.5}
    Alien couples always consist of one left-handed partner and one-right handed partner.
    \begin{enumerate}[a)]
        \item An alien claims to be from Mars, but their partner claims they're lying. Are these aliens from the same planet?
        \item One member of an alien couple asserts they're both from Venus while the other says that's not true. Which of these aliens is right handed?
        \item One member of another couple says their partner is from Mars. The other says they are both from Mars. What is the planet of origin and the handedness of each of them?
    \end{enumerate}
\end{prob}

\end{document}